### 2010-02-11 doc/manuals/configuration/configuration_manual.tex
Making it possible to load a profile by only specifying its name.

A INI configuration file basically consist of sections, attribute-value pairs
and maybe comments and blank lines. In the following code-listing the syntax of
an INI configuration file is shown:
\begin{lstlisting}
# A comment
[ common ]
profile = <path-to-profile>

@@

The \texttt{profile} attribute is also a special, as it is used to indicate
which profile the INI configuration uses, and its value should be the
absolute path to the profile file. The \texttt{profile} attribute must be
located in the common section. If multiple \texttt{profile} attributes exist
only the first attribute will be used.

>>>>

A INI configuration file basically consist of sections, attribute-value pairs
and maybe comments and blank lines. In the following code-listing the syntax of
an INI configuration file is shown:
\begin{lstlisting}
# A comment
[ common ]
profile = <profilename> or <path-to-profile>

@@

The \texttt{profile} attribute is also special, as it is used to indicate
which profile the INI configuration uses. Its value should either be the name of
a WS-ARC profile (no \texttt{xml} suffix), see
appendix~\ref{app:List of profiles} or it should be the absolute path to a
profile (with \texttt{xml} suffix). The \texttt{profile} attribute must be
located in the common section. If multiple \texttt{profile} attributes exist
only the first attribute will be used.
